---
title: "Untitled"
output: powerpoint_presentation
date: "2026-05-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(plotly)
library(tidyr)
sec_eb <- readRDS("all_data.RDS")

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = FALSE}
df <- sec_eb %>% filter(Q %in% c("Q01.1. How interested would you say that you are in the following? - Politics in the UK"),  
                                 # "Q01.2. How interested would you say that you are in the following? - Politics in my local area" ),
                        Question %in% c("NET: Interested", "NET: Not Interested" ),
                        x %in% c("Total", "London")
                        )

plot_df <- df %>% select(Question, x, prc_calc) %>% 
  pivot_wider(names_from = x, values_from = prc_calc)

plot_ly(plot_df, type = "bar", x = ~Question, y =~ Total, name = "UK" ) %>% 
  add_trace(y = ~London, name = "London")


df <- sec_eb %>% filter(Q %in% c("Q01.2. How interested would you say that you are in the following? - Politics in my local area" ),
                        Question %in% c("NET: Interested", "NET: Not Interested" ),
                        x %in% c("Total", "London")
                        )

plot_df <- df %>% select(Question, x, prc_calc) %>% 
  pivot_wider(names_from = x, values_from = prc_calc)

plot_ly(plot_df, type = "bar", x = ~Question, y =~ Total, name = "UK" ) %>% 
  add_trace(y = ~London, name = "London")
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

